A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-30 paper/paper.tex
paper: include table in Overture

\iffalse
  Our contribution is the following. We have modelled the core of semi-simplicial sets in a way that naturally generalizes to semi-cubical sets in type theory, and we call our generalization \emph{$\nu$-sets}. In contrast to the presheaf presentation of semi-cubical -based where the set of  that use a fibered representation, we use an indexed representation. Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.

  \begin{table}[H]
    \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
      \toprule
              & Set theory & Type theory \\
      \graymidrule
      Fibered & CCHM       &             \\
      \graymidrule
      Indexed &            & Our work    \\
      \bottomrule
    \end{tabularx}
  \end{table}

  Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT. The most significant implementation of cubical type theory in the real world is a branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}. Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
\fi

>>>>

\iffalse
  Our contribution is the following. We have modelled the core of semi-simplicial sets in a way that naturally generalizes to semi-cubical sets in type theory, and we call our generalization \emph{$\nu$-sets}. In contrast to the presheaf presentation of semi-cubical -based where the set of  that use a fibered representation, we use an indexed representation. Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.
\fi

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
    \toprule
            & Set theory     & Type theory \\
    \graymidrule
    Fibered & \cite{Cohen16} &             \\
    \graymidrule
    Indexed &                & Our work    \\
    \bottomrule
  \end{tabularx}
\end{table}
